Co-moving stars in \textsl{Gaia DR1}: a catalog of genuine comoving star pairs from low-resolution spectroscopic follow-up

### 2017-06-03 paper/comoving-followup.tex
smooth the spectra

This wavelength calibration procedure produces a nightly model for the
nonlinear dispersion of wavelength as a function of pixel value for each
extracted 1D spectrum.
However, because of flexure in the spectrograph, each observation will have an
additional, unknown constant offset of, typically, $\approx 0.5$--$2~{\rm
\AA}$, corresponding to a significant velocity offset at ${\rm H}\alpha$ of
$\approx 20$--$100~\kms$.
\figurename~\ref{fig:sample-spectra} shows a random sample of 10 source spectra
of comoving star pair members normalized to 1 at $\lambda = 5500~{\rm \AA}$ and
shifted by index for visualization.
From the appearances of these 10 spectra, it seems there is a mix of
metallicities and spectral types amongst the observed targets.
Note that the spectra are not flux-calibrated, as we only care about measuring
radial velocities from this sample.

>>>>

This wavelength calibration procedure produces a nightly model for the
nonlinear dispersion of wavelength as a function of pixel value for each
extracted 1D spectrum.
However, because of flexure in the spectrograph, each observation will have an
additional offset of, typically, $\approx 0.5$--$2~{\rm \AA}$, corresponding to
a significant velocity offset at ${\rm H}\alpha$ of $\approx 20$--$100~\kms$.
\figurename~\ref{fig:sample-spectra} shows a random sample of 10 source spectra
of comoving star pair members normalized to 1 at $\lambda = 5500~{\rm \AA}$ and
shifted by index for visualization.
From the appearances of these 10 spectra, it seems there is a mix of
metallicities and spectral types amongst the observed targets.
Note that the spectra are not flux-calibrated, as we only care about measuring
radial velocities from this sample.
